### 2017-04-06 paper/evaluation.tex
RQ6 - subsection for tradeoffs
pass on RQ3

To answer \numRQD{}, we considered \emph{all} \numProjectsPar{}
subjects from our benchmark that use parallelization by default in
Maven to run tests.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects. For each project, the
speedup (or slowdown) corresponds to the ratio ($T_s/T_p$) between the
elapsed time of a sequential execution ($T_s$) and the elapsed time of
a corresponding parallel execution ($T_p$), obtained as described in
the script from Figure~\ref{fig:mvn-execution}.  As usual, a ratio
above 1x denotes speedup and a ratio below 1x denotes slowdown.

%% For each project, we modified the existing configurations to disable
%% the parallel test execution. In addition, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

@@

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names, which appear in bold.  Columns
``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
project group and the name of the subject.  Column ``$T_s$'' shows
sequential execution time whereas column ``$T_p$'' shows parallel
execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
associated with parallel execution.

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
three extreme cases: \CodeIn{Chaos}, \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first, the default configuration is \textbf{C2}, however, the test is
composed of takes $>$99\% of the test time. In this case, when running
in sequential the execution time is almost the same as the parallel
execution.
The second when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods. In this case, a high slowdown is noticed when running those
big methods sequentially.
The third, runs parallel configuration in \Fix{80\%} of the project
modules, however, the test time is dominated by one of the
sequentially running modules.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQD{}:}~\emph{Overall, results indicate
      that the speedup obtained with parallelization is
      \Fix{$\sim$x\%} (in average) for \Fix{\%} of the projects
      (\Fix{x} out of \Fix{w}). }
  \end{minipage}
}
\end{center}

@@

\Fix{discuss trade-offs and elaborate conclusion....}

>>>>

To answer \numRQD{}, we considered \numProjectsPar{} subjects from our
benchmark that use parallelization \emph{by default} when running
tests.  In those projects, parallelization is active without passing
any extra parameters.  Section~\ref{sec:rqC-1} describes in detail the
methodology we used to find these subjects and
Section~\ref{seq:rq6-tradeoffs}, we verified that both
%% executions produce the same outcome to eliminate noise from failing
%% tests.  To compute the speedup, we divide the time obtained in the
%% sequential execution by the time obtained from the default execution.
%% For instance, if a project runs the tests sequentially in $10m$ and
%% the same execution runs in $5m$ with parallelization enabled (default
%% execution), the speedup is two.

@@

Figure~\ref{tab:speedup} summarizes results.  Lines are sorted by
abbreviated project names, which appear in bold.  Columns
``\emph{Group}'' and ``\emph{Name}'' indicate, respectively, the
project group and the name of the subject.  Column ``$T_s$'' shows
sequential execution time whereas column ``$T_p$'' shows parallel
execution time. Column ``$T_s/T_p$'' shows the speedup or slowdown
associated with parallel execution.   As usual, a ratio
above 1x denotes speedup and a ratio below 1x denotes slowdown.

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  Three
cases worth special attention: \CodeIn{Chaos}, \CodeIn{Jcabi} and
\CodeIn{Log4J2}.  No significant speedup was observed in
\CodeIn{Chaos}, a project with only three test classes, of which one
monopolizes the bulk of test execution time.  This project uses
configuration \ParClassSeqMeth{}, which runs test classes in parallel
and test methods, declared in each class, sequentially.  Consequently,
speedup cannot be obtained as the cost of the single expensive test
class cannot be broken down with the selected configuration.  Although
project \CodeIn{Jcabi} also uses configuration \ParClassSeqMeth{},
results obtained are very different compared to \CodeIn{Chaos}.  The
speedup observed in \CodeIn{Jcabi} was the highest amongst all
projects.  This project contains test classes with a small number of
test methods and several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.  Finally, we note that parallel
execution in \CodeIn{Log4J2} was innefective.  We found that Maven
invokes several test modules in this project but the test modules that
dominate execution time run sequentially by default.

%% The third, runs parallel configuration in
%% \Fix{80\%} of the project modules, however, the test time is dominated
%% by one of the sequentially running modules.  \Luis{$\leftarrow$ rework
%%   this} \Fix{falar sobre o resultado geral dos speedups - elaborar
%%   menor e maior speedup... acho que so vale a pena discutir quando
%%   tiver conviccao dos 2 casos}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQD{}:}~\emph{ The average speedup observed
      with default configurations of parallelization was
      \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

@@

\subsubsection{Trade-offs}
\label{seq:rq6-tradeoffs}
\Fix{discuss trade-offs and elaborate conclusion....}
